Continuous Generalization of Buildings

### 2017-03-31 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
having written down our basic idea; implementing our method

\pgfplotsset{
	compat=newest,
	xlabel near ticks,
	ylabel near ticks
}
\newcommand{\Astar}{A$^{\!\star}$\xspace}
\newcommand{\tstar}{\ensuremath{t\xspace}}
\newcommand{\Pistar}{\ensuremath{\Pi}} % {\Pi_{\mathrm{start}}(\tstar)}
\newcommand{\Pstart}{\ensuremath{\mathpzc{P}_\mathrm{start}}\xspace}
\newcommand{\Pgoal}{\ensuremath{\mathpzc{P}_\mathrm{goal}}\xspace}
\newcommand{\Pnode}{\ensuremath{\mathpzc{P}_{t,i}}\xspace}
\newcommand{\Tgoal}{\ensuremath{T_\mathrm{goal}}\xspace}

@@

\newcolumntype{x}[1]{>{\raggedleft\arraybackslash\hspace{0pt}}b{#1}}
\newcolumntype{y}[1]{>{\centering\arraybackslash\hspace{0pt}}b{#1}}
%\newcolumntype{y}[2]{>{\centering\arraybackslash\hspace{0pt}}D{.}{.}{#1}b{#2}}
%\newcolumntype{d}[1]{D{.}{.}{#1}}
\newcolumntype{L}{>{$}l<{$}}% math-mode version of "l" column 
%type
\newcolumntype{R}{>{$}r<{$}}% math-mode version of "r" column 
%type
\newcolumntype{C}{>{$}c<{$}}% math-mode version of "c" column 
%type

%This style looks better than $\mathrm{non-comp}$ in which "-" 
%looks like the symbol of minus 
\newcommand\nonhyphencomp{\operatorname{non-comp}}
\newcommand\inthyphenleng{\operatorname{int-leng}}
\newcommand\goalhyphentype{\operatorname{goal-type}}
\newcommand\goalhyphennon{\operatorname{goal-non}}
\newcommand\goalhyphenshape{\operatorname{goal-shape}}
%\newcolumntype{y}[1]{>{\raggedleft\arraybackslash\hspace{0pt}}p{#1}}
%\newcolumntype{x}[1]{>{\centering\arraybackslash\hspace{0pt}}p{#1}}

@@

\newcommand{\myabstract}{text}

@@

@@

Text

>>>>

\pgfplotsset{
	compat=newest,
	xlabel near ticks,
	ylabel near ticks
}

@@

@@

\newcommand{\myabstract}{We proposed a method to continuous 
generalization of buildings from a start scale to a goal scale. 
%
For each building at the start scale, we generate its 
generalized form at 
the goal scale by enlarging and simplifying. Then we grow the  
building to the 
generalized form to realize continuous transformation. During 
the 
growing, we aggregate two buildings once they become too close 
to each other. We generate a new generalized form at the goal 
scale for 
the aggregated building so that we can continue growing.
%
After finishing the growing, we take the goal scale as the 
start scale and repeat our continuous generalization. The start 
scale and the target scale should not be too far away because we 
want the intermediate results to be somewhat simplified.

Our contribution is as follows. First, the buildings 
are enlarged continuously and at the same time are simplified. 
Second, the distance between each pair of two buildings is 
always larger than a specified distance. Third, there is no thin 
part in our results.}

%We proposed a method to continuous 
%generalization of buildings from a start scale to a goal scale. 
%%
%For each building at the start scale, we enlarge it by 
%buffering. We simplify the enlarged building by the operator of 
%dilation-erosion-erosion-dilation. Then we merge the 
%simplified form with the original 
%building so that the merged result completely contains the 
%original 
%shape. We use the merged shape as the building at the goal 
%scale, and grow the original building to the 
%goal shape to realize continuous transformation. 
%%
%During the 
%growing, if two buildings become too close to each other, we 
%aggregate them to avoid narrow gap. To aggregate, we dilate and 
%merge the two buildings, then we erode the merged shape. To 
%avoid 
%failure or thin parts from the aggregation, we construct a 
%skeleton of the dilated and merged form. We make a buffer of 
%the 
%skeleton 
%and merge the buffer with the eroded shape. We take the 
%aggregated shape which may be merged with the skeleton buffer 
%as 
%a new 
%building and generate its goal shape at the goal scale so that 
%we can grow this new building.
%
%Once we arrive at the goal scale, we take the goal scale as the 
%start scale and repeat our continuous generalization. The start 
%scale and the target scale cannot be too far away because we 
%want to see some simplification during the growing of buildings.
%%
%There are several advantages of our method. First, the 
%buildings 
%are enlarged continuously and the same time are simplified. 
%Second, the distance between each pair of two buildings is 
%always larger than a specified distance. Third, there is no 
%thin 
%part in our results.

@@

Straight skeletons for map generalization: 
\textcite{Gold2003,Matuk2006}

Geometric Simplication of Administrative Borders With Mixture of
Irregular and Orthogonal Segments \parencite{Samsonov2016}

\citetitle{Damen2008} \parencite{Damen2008}

@@

Because of our aggregation with skeletons and original 
buildings, we may have too many details in the intermediate 
results.

Some buildings are too small to be eroded. We have to generate 
squares or MBR?

To make it more efficient for on line displaying, we may need 
some external memories. First, we store the data at some key 
scales so that we may start a generalization from the immediate 
larger scale; $O(n)$ space. Second, we store the target shape 
for each building; $O(n)$ space. Third, we store the aggregation 
time and the target form for the aggregated shape; $O(n^2)$ 
space if we count vertex number.
%
The displaying time is dependent on buffering and clipping. The 
two operators are from library Clipper. The efficiency of the 
buffering function of this library has been evaluated by 
\textcite{Palfrader2015}.

One can also discuss about our growing speed.
